---
title: "Practical Machine Learning"
author: "lywen"
date: "2015年6月10日"
output: html_document
---
###  using KNN Modeling, and got the KNN model sample error is 10%.   
### loading the data
```{r}
##setwd('~/desktop/ML')
testsets <- read.csv("pml-testing.csv")
testsets=testsets[,-1]
trainsets <- read.csv("pml-training.csv")
trainsets=trainsets[,-1]

```
Delete the factor or the string variables from test and train datasets;then eliminate the variables from the new train dataset over half  of length variable is NA.
```{r}
variables=which(sapply(trainsets,class)%in%c('integer','numeric')&sapply(trainsets,function(data)ifelse(sum(!is.na(data))>length(data)/2,TRUE,FALSE)))
newtrain=trainsets[,variables]
newtrain=sapply(newtrain,
                function(data)
                  (data-min(data,na.rm=T))/(max(data,na.rm=T)-min(data,na.rm=T)))
```
### dividing the newtrain dataset 60% for training,40% testing.

```{r}
index=sample(dim(newtrain)[1],size=0.6*dim(newtrain)[1],replace=F)
training=newtrain[index,]
testing=newtrain[-index,]
```
###  Build KNN model with  training datsets
```{r}
library(class)
predicted=knn(training,testing,trainsets$classe[index],k=10)
real.train=trainsets$classe[-index]
```
### Calculate the errors of the Cross Validation Set.
```{r}
SampleError=1-sum(predicted==real.train)/length(predicted)
```
###  So the Out of Sample Error is: `r SampleError`  
###  Predict testing data   
```{r}
newtset=sapply(testsets[,variables],
                function(data)
                  (data-min(data,na.rm=T))/(max(data,na.rm=T)-min(data,na.rm=T)))
results <- knn(newtrain,newtset,trainsets$classe,k=10)
results
```

